\documentclass[12pt]{article}
% \usepackage[utf8]{inputenc}

\usepackage{jstav}

% specifies doc title
\title{Personal \LaTeX Style File}
\author{Jacob Stavrianos}

% begin the document
\begin{document}

% actually insert the title.
\maketitle

\section*{Overview}
This project provides a general-purpose style file to be imported into other overleaf projects. Overleaf supports sharing files from other projects, live-syncing upon changes to the original project. It \textit{doesn't} conveniently support links to auxiliary files in the original project. so I chose to write the entire project into a single, monolithic style file.

The file \texttt{jstav.sty} provides the package \texttt{jstav}, which can be both shared to other projects and imported (within a project) to \texttt{.tex} or \texttt{.sty} files. It incorporates all the packages, macros, and formatting I'm used to writing latex with. The style file can't be edited in different projects, but can be overwritten by a wrapper style file.

\section*{Usage}

\begin{itemize}
    \item [Overleaf: ] Import \texttt{jstav.sty} via the ``upload'' icon in the top-left corner.
    \item [Raw TeX: ] Treat \texttt{jstav.sty} as a textfile that, when compliled as TeX, provides the \texttt{jstav} package. Practically speaking, download \texttt{jstav.sty} to the desired directory (somewhere in the package path) and import \texttt{jstav} as normal.
\end{itemize}

To include the \texttt{jstav} package as style, use the following TeX command: \texttt{\textbackslash usepackage\{jstav\}}

\end{document}